\dish{Bagels}
%\altdish{}
%\serves{}
\makes{12}
\prep{2 hours}
\source{unknown}

\begin{ingredients}
  \ingr{1\fracH}{c}{warm water}
  \ingr{2\fracQ}{\tsp}{baking yeast}
  \ingr{4}{c}{flour}
  \ingr{2}{\tbsp}{malt syrup}
  \ingr{2}{\tsp}{kosher salt}
  \ingr{4}{\tsp}{granulated sugar}
  \ingr{1}{}{egg white}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Dissolve yeast in water, set aside.

  \item In a stand mixer fitted with dough hook, combine remaining
    ingredients except egg.  Add yeast mixture.  Knead.  The dough
    should be dry, not tacky or sticky, and somewhat stiff.

  \item Shape the dough into a ball, place it in a large oiled bowl,
    and turn it to coat in oil. Cover the bowl with a damp towel and
    let the dough rise in a warm place, until it is noticeably puffy
    and springs back when you poke it, about 20 minutes. (The dough
    will not double in size.)

  \item While the bagels are rising,
    \begin{itemize}
      
    \item Preheat the oven to 220\degreeC\ with rack in the middle.

    \item Fill a large, wide, shallow pan (about 3 to 6 quarts) with
      water, bring to a boil over high heat, then reduce heat to
      medium low and let simmer. Cover until ready.

    \item Line a baking sheet with parchment paper greased with
      oil.

    \item Place a metal rack inside of a second baking sheet and set
      aside.

    \end{itemize}

  \item Turn the risen dough out onto a dry surface and divide into
    12~equal pieces.  Roll each piece into a rope about 20--25~cm
    long, lightly moisten the ends with water, overlap the ends by
    2--3~cm, and press to join. Widen the hole in the middle to 2~cm
    if necessary.  Cover the shaped bagels with a damp towel and let
    rest 10~minutes.

  \item After resting, stretch the dough to retain the 2--3~cm hole
    and boil the bagels several at a time, making sure they have room
    to bob around. Cook 30~seconds on each side, until they have a
    shriveled look.  Remove to the baking sheet with the rack in
    it. Adjust heat as necessary so the water stays at a simmer.

  \item Whisk together one \tbsp\ water and the egg white. Brush the
    bagels with the egg wash.  Sprinkle topping if desired.

  \item Arrange the bagels on the baking sheet lined with parchment
    paper about 2--3~cm apart and bake. Rotate the pan after 15 minutes
    and bake until the bagels are a deep caramel color and have formed
    a crust on the bottom and top, about 10~minutes more.

  \item Remove from the oven and let cool on a rack for 30~minutes so
    the interiors finish cooking and the crusts form a chewy exterior.

  \end{enumerate}
\end{recipe}
