\dish{Levain bagels}
\altdish{Bagels, levain}
%\serves{}
\makes{4--6}
\prep{30 minutes + 16 hours}
\source{modernist.bread}

\begin{ingredients}
  \ingr{135}{ml}{water}
  \ingrS{188}{g}{levain}
  \ingr{375}{g}{bread flour}
  \ingr{19}{g}{sugar}
  \ingr{13}{g}{vegetable oil}
  \ingr{10}{g}{salt}
  \ingrS{9}{g}{malt syrup}
  \ingr{\bf Lye solution}{}{}
  \ingr{4}{L}{water}
  \ingrS{6}{g}{lye}
\end{ingredients}

\begin{recipe}
  \begin{enumerate}

  \item Combine water and levain, then remaining ingredients except
    lye solution.  Mix on low speed to medium gluten development, then
    on medium speed to full gluten development.

  \item Lightly oil, cover, and bulk ferment for one hour.

  \item Divide and roll into balls.  Then pull each ball around itself
    from the ``corners'' to create uniform tension in the dough.
    Allow to rest 20~minutes.

  \item Use a wooden spoon handle to poke a hole in each ball, then
    roll around the hole to create a bagel shape.

  \item Place on parchment paper dusted with corn meal and allow to
    rise, uncovered, refrigerated, overnight (for 12--16 hours at
    4\degreeC, for 2\fracH--3\fracH~hours at 21\degreeC, or for
    2--2\fracH~hours at 27\degreeC).

  \item Bring the lye solution to a boil.  Boil each bagel for about
    1~minute (30~seconds on each side).  Return to parchment lined
    sheet pans.

  \item Bake at 220\degreeC{} for 10--12~minutes with convection or
    230\degreeC{} and 12--15 minutes without.

  \end{enumerate}
\end{recipe}
