\dish{Corn bread}
%\altdish{}
\serves{4--8}
%\makes{}
\prep{15 minutes + 15 minutes baking}
\source{joy}

\begin{ingredients}
  \ingrS{2}{}{eggs, separated}
  \ingr{\fracQQ}{c}{T65 flour (T55 ?)}
  \ingr{1}{\tsp}{baking powder}
  \ingr{1}{\tbsp}{sugar}
  \ingrS{\fracQQ}{\tsp}{salt}
  \ingrS{1\fracQ}{c}{corn meal (stone ground)}
  \ingrS{1\fracH}{c}{cream, whipped}
  \ingrS{3}{\tbsp}{butter, melted}
  \ingr{}{}{butter (for the skillet)}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Place an iron skillet in the oven and preheat to 220\degreeC{}.

  \item Separate eggs.  Begin whipping whites into meringue and yolks
    into a pale foam.

  \item Sift together flour, baking powder, sugar, and salt.  Mix in
    corn meal.  Set aside.

  \item Whip cream.

  \item Combine ingredients, working the dough as little as possible.

  \item Remove the hot skillet from the oven, place extra butter in it
    and allow to melt and brown, then pour batter into the skillet and
    cover.  Place back in oven.

  \item Cook 20--25~minutes (15~minutes for bread stick or mini-muffin
    format).

  \item Remove from skillet and place on a wire rack to cool only
    slightly, then consume warm from the oven (with more butter).

  \end{enumerate}
\end{recipe}

\notes
Variants:
\begin{itemize}
\item Replace a \fracH cup of corn meal with a same quantity of
  buckwheat.
\item Use no sugar or substitute brown sugar.
\item Add minced onions.
\item Add shredded cheddar cheese.
\item Add maize.
\item Vary the proportions of flour and corn meal.
\end{itemize}

%\accord{}

% This recipe is modified by Jeff Abrahamson based on the ``skillet corn
% bread'' recipe in \textit{Joy of Cooking}.
%
% The original:
%
% Sift together
%   3/4 c sifted all purpose flour
%   2 1/2 tsp baking powder
%   1-2 Tbsp sugar
%   3/4 tsp salt
%
% Add
%   1 1/4 c cornmeal
%
% In a separate bowl, beat
%   1 egg
% then add
%   2-3 Tbsp melted butter
%   1 c milk
