\dish{Laugenecken}
%\altdish{}
%\serves{}
\makes{8}
\prep{90 minutes over 3 hours}
\source{internet}

\begin{ingredients}
  \ingr{12}{g}{dry yeast}
  \ingr{10}{ml}{whole milk, warm}
  \ingrS{1}{\tsp}{honey}
  \ingr{450}{g}{flour T55}
  \ingr{100}{ml}{buttermilk}
  \ingr{1}{}{egg}
  \ingr{2--3}{g}{salt (\fracH{} \tsp)}
  \ingrS{60}{g}{butter, softened}
  \ingrS{80}{g}{butter, softened, for the disks}
  \ingrS{}{}{large crystal salt for topping}
  \ingr{6}{g}{lye}
  \ingrS{1.5}{litres}{water}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Dissolve yeast in warm milk with honey.

  \item Add remaining ingredients and knead.  Place in covered bowl
    for about an hour.

  \item Divide dough into 8~equal pieces (about 100~g each) and roll
    into balls.

  \item One by one, roll the balls into disks about 20 cm in diameter,
    buttering the top of each disk (except the last one), stacking and
    pressing firmly so that they adhere.

  \item Roll the stack to compress them slightly and to make them a
    bit larger.  Place on a floured plate and refrigerate 20~minutes,
    covered.

  \item Cut stacked disk into 8~wedges, separating each slightly from
    its neighbours, and applying slight pressure to each piece to bind
    together any ragged edges.

  \item Allow to rise 20~minutes.

  \item Dissolve lye in water.  Preheat oven to 180\degreeC{}
    (ventilated) or 200\degreeC{} (non-ventilated).

  \item Dip the wedges in the lye, then place on a parchment-lined
    baking sheet.

  \item Sprinkle with large crystal salt.

  \item Bake 15--18~minutes, then place on wire rack.

  \end{enumerate}
\end{recipe}

%\accord{}
