\dish{Laugenecken}
%\altdish{}
%\serves{}
\makes{8}
\prep{90 minutes over 12 hours}
\source{internet}

\begin{ingredients}
  \ingr{5}{g}{dry yeast}
  \ingr{220}{ml}{whole milk, warm}
  \ingrS{1}{\tsp}{honey}
  \ingr{500}{g}{flour T65}
  \ingr{1}{}{egg}
  \ingrS{1}{\tsp}{salt (6~g?  should be 10~g?)}
  \ingrS{70}{g}{butter, softened}
  \ingrS{50--75}{g}{butter, softened, for the disks}
  \ingr{6}{g}{lye}
  \ingrS{1.5}{litres}{water}
  \ingr{}{}{large crystal salt for topping}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Dissolve yeast in warm milk with honey.

  \item Add remaining ingredients and knead.  Place in covered bowl in
refrigerator overnight.

  \item Divide dough into 8~equal pieces (about 100~g each) and roll
into balls.

  \item One by one, roll the balls into disks about 20 cm in diameter,
buttering the top of each disk (except the last one), stacking and
pressing firmly so that they adhere.  Cut stacked disk into 8~wedges,
separating each slightly from its neighbours, and applying slight
pressure to each piece to bind together any ragged edges.

  \item Allow to rise 30~minutes.

  \item Dissolve lye in water.  Preheat oven to 200\degreeC.

  \item Boil the wedges in the lye for 45~seconds each, placing on a
parchment-lined baking sheet.

  \item Sprinkle with large crystal salt.

  \item Bake 15--20~minutes, then place on wire rack.

  \end{enumerate}
\end{recipe}

\notes
\begin{itemize}
\item I used 100~ml cream and 120~ml milk, reducing the flour by
  20~g.  To test.
\item I invented the quantity of lye here based on bagels (1.5~g/L)
  rather than pretzels (30~g/L).
\item It may be worth testing whether it's better with or without
  honey.
\item It may be worth experimenting with loading temperature vs
  backing temperature.
\end{itemize}

%\accord{}
