\dish{Roggenbrot}
\altdish{Pain de seigle}
\altdish{Bread, rye}
%\serves{}
\makes{500 g}
\prep{6 hours}
\source{modernist.bread}

\begin{ingredients}
  \ingr{95}{ml}{warm water}
  \ingrS{1.5}{g}{instant dry yeast}
  \ingr{220}{g}{liquid rye levain, mature (2 parts rye flour to 3 parts water)}
  \ingr{220}{g}{light rye flour}
  \ingr{15}{g}{gluten}
  \ingr{15}{g}{bread flour (T65)}
  \ingr{6}{g}{salt}
  \ingr{2}{g}{aniseeds, ground}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Mix water and dry yeast to dissolve.  Add remaining
    ingredients and mix.  Transfer to a lightly oiled bowl and cover
    with lid or plastic film.
    
  \item Bulk fermentaton 2.5 hours, folds after 1~and 2~hours.
    
  \item Preshape, let reste 15--20 minutes.
    
  \item Shape into bâtard (or boule).  Allow to proof 1.5--2 hours.
    
  \item Preheat oven to 240\degreeC.
    
  \item Score.  Bake at 240\degreeC{} (loading temperature) then
    180\degreeC{} (baking temperature) for 30--35 minutes.

  \item Cool on wire rack.  Allow at least 10~minutes before cutting.
    
  \end{enumerate}
\end{recipe}

\stage{Teeroggenbrot (Pu-Ehr)}

Replace the 95~ml of warm water with 95 ml of strong Pu-Ehr tea (6 g
of tea leaves in 120 ml of water infused at 95\degreeC{} for
60~seconds).  Allow to cool to 50\degreeC{} before adding yeast.

\stage{Teeroggenbrot (Oolong Fu Lian)}

Replace the 95~ml of warm water with 95 ml of strong Oolong Fu Lian
tea (7.5~g of tea leaves in 125~ml of water infused at room
temperature for 45~minutes).

%\accord{}
