\dish{American Apple Pie}
\altdish{Pie, apple}
\altdish{Apple Pie}
%\serves{}
\makes{1 pie}
\prep{15 minutes plus various resting and baking times}
\source{rosie}

\begin{ingredients}
  \ingr{6--8}{}{Granny Smith apples (8 cups)}
  \ingr{\fracQQ}{c}{sugar}
  \ingr{1}{\tbsp}{cinnamon}
  \ingr{\fracH}{\tsp}{nutmeg}
  \ingr{\fracQ}{\tsp}{salt}
  \ingr{\fracQ}{c}{apple cider, apple juice, or orange juice}
  \ingr{2}{\tbsp}{fresh lemon juice}
  \ingr{1\fracH}{\tbsp}{corn starch}
  \ingr{1}{\tbsp}{butter}
  \ingr{1}{}{egg mixed with 2 \tbsp~water or milk for glazing}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Prepare a double crust pie crust, page~\pageref{pie-crust}.
    Place one crust in the pie plate and refrigerate both crusts.

  \item Preheat oven to \FC{450}{232}.

  \item Peel, core, and cut apples into \fracEE-inch slices.  Place in
    a large bowl with remaining ingredients except the butter and the
    glaze.  Toss together with hands to coat the apples evenly.
    
  \item Scoop the apples into the bottom crust and dot the mixture
    with small pieces of butter.

  \item Cover the apples with the top crust.  Seal and trim the edge.
    Make the edge pretty.  Cut a few slits in the top crust.  Brush
    the top crust with the egg.

  \item Bake 15~minutes, then reduce heat to \FC{350}{177} and
    continue baking until the pie is golden and the filling is
    bubbling, about 1~hour~and 10~minutes longer.  If the top crust is
    getting too dark, cover it with a piece of aluminium foil and
    continue to bake.

  \item Remove from the oven and cool on a rack.  Serve with vanilla
    ice cream.

  \end{enumerate}
\end{recipe}
