\dish{Banana Cake with Cinnamon and Chocolate}
\altdish{Cinnamon and Chocolate Banana Cake}
\altdish{Chocolate and Cinnamon Banana Cake}
\altdish{Cake, Banana with Chocolate and Cinnamon}
%\serves{}
\makes{one $9\times 13$ pan}
\prep{30 minutes + 1 hour to bake}
\source{jma}

\begin{ingredients}
  \ingr{2 \fracQ}{c}{plus 5 Tbsp flour, sifted}
  \ingr{1 \fracH}{tsp}{baking soda}
  \ingr{\fracH}{tsp}{salt}
  \ingr{230}{g}{yogurt (1 cup)}
  \ingr{5}{}{very ripe bananas (skins should be brown)}
  \ingr{150}{g}{unsalted butter}
  \ingr{80}{g}{vegetable oil}
  \ingr{300}{g}{brown sugar}
  \ingr{1}{tsp}{vanilla extract}
  \ingr{3}{}{large eggs}
  \ingr{}{}{cinnamon and sugar (50/50 mixture)}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Preheat oven to 350\F.  Lightly butter a $13\times 9$ inch
    baking pan.

  \item Sift flour, baking soda, and salt together into a small bowl
    and set aside.

  \item In a second small bowl, mash bananas, then stir in the yogurt.

  \item Cream butter, oil, sugar, and vanilla until light and fluffy,
    about 2 minutes.  Add the eggs one at a time and beat on medium
    until blended, about 10 seconds each.

  \item With the mixer on low speed or mixing by hand, add one third
    of the dry ingredients, then half the banana mixture, then the
    remainder of the dry, then the remainder of the banana.  Stir 8-10
    seconds after each addition.  Stir by hand if necessary to mix
    thoroughly.

  \item Pour batter into the prepared pan.  Cover with a thick layer
    of cinnamon and sugar.

  \item Bake at {350\F} until the cake springs back to the touch and a
    tester inserted in the center comes out dry, about 1 hour 10
    minutes.

  \item Cool on a wire rack.  When cool, frost with chocolate frosting (below).

  \end{enumerate}
\end{recipe}


\textbf{Chocolate frosting:}

\begin{ingredients}
  \ingr{220}{g}{dark chocolate}
  \ingr{100}{g}{butter}
  \ingr{2}{Tbsp}{heavy cream}
  \ingr{2}{Tbsp}{cocoa (optional)}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Gently melt butter and chocolate.  Mix in cream.  If desired,
    stir in the cocoa (or reserve to dust on top of the frosted cake).

  \item Frost the cake.  Dust with cocoa if desired.  Allow to rest at
    least an hour before serving.

  \end{enumerate}
\end{recipe}

