\dish{Dark Chocolate Mousse}
\altdish{Chocolate Mousse, dark}
\altdish{Mousse, chocolate}
\makes{4 cups}
\prep{1 hour plus several hours to set}
\source{ghirardelli-insert}

\begin{ingredients}
  \ingr{4}{}{egg yolks}
  \ingr{\fracH}{c}{sugar}
  \ingr{2 \fracH}{c}{heavy cream}
  \ingr{6}{oz}{unsweetened chocolate, broken in chunks}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Beat egg yolks until light.  Gradually add sugar.

  \item Heat one cup of the cream over low heat until warm.  Gradually
    add half to the egg mixture and mix, then combine back to the warm
    cream.

  \item Cook over low heat, stirring constantly, until mixture
    thickens.

  \item Let cool several minutes, then add chocolate and stir until
    chocolate is melted and mixture is uniform.  Cool until no longer
    warm.

  \item Beat remaining cream until stiff.  Mix half into chocolate,
    then fold the remainder into the chocolate.

  \item Spoon into cups and refrigerate for at least several hours to
    set.

  \end{enumerate}

Notes:
\begin{itemize}
\item I found the chocolate mixture to be too thick, so I added two or
  three heaping tablespoons of ricotta.

\item The original recipe suggested ten minutes cooling before adding
  the chocolate and two hours of cooling in the refrigerator before
  adding the cream.  This seemed orders of magnitude excessive to me:
  a couple minutes sufficed.

\item Before refrigerating, grate some 85\% chocolate on top and maybe
  a tiny zest of orange rind for color.
\end{itemize}

\end{recipe}
