\dish{Chocolate Orgasms}
\altdish{Brownies, chocolate orgasms}
\makes{9--12 large brownies}
\prep{30 minutes plus 30 minutes to bake, 1 hour to cool, one day to set}
\source{rosie}

\stage{Brownies}

\begin{ingredients}
  \ingr{3\fracH}{oz}{unsweetened chocolate}
  \ingr{6}{oz}{unsalted butter, at room temperature}
  \ingr{1\fracH}{c}{sugar}
  \ingr{\fracQQ}{tsp}{vanilla}
  \ingr{3}{}{large eggs, at room temperature}
  \ingr{\fracQQ}{c}{plus 2 Tbsp flour}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}
  \item Preheat oven to 350 F.  Lightly grease an 8 inch square pan
    with butter or vegetable oil.

\item Melt the chocolate and butter in the top of a double boiler
  placed over simmering water.  Cool the mixture for 5 minutes.

\item Place  the sugar in  a medium-size mixing  bowl and pour  in the
  chocolate  mixture.  Using an  electric mixer  on medium  speed, mix
  until  blended, about  25 seconds.   Scrape the  bowl with  a rubber
  spatula.

\item Add the vanilla.  With the mixer on medium-low speed, add the
  eggs one at a time, blending after each addition until the yolk is
  broken and dispersed, about 10 seconds.  Scrape the bowl after the
  last egg and blend until velvety, about 15 more seconds.

\item Add the flour on low speed and mix for 20 seconds; finish the
  mixing by hand, being certain to mix in any flour at the bottom of
  the bowl.

\item Spread the batter evenly in the prepared pan.

\item Bake the brownies on the center oven rack until a thin crust
  forms on top and a tester inserted in the center comes out with a
  moist crumb, 25 to 30 minutes.

\item Remove the pan from the oven and place it on a rack to cool for
  1 hour before cutting the brownies.  Serve the next day (it takes a
  day for the flavor to set).

  \end{enumerate}
\end{recipe}
                                                                               

\stage{Frosting}

\begin{ingredients}
\ingr{1}{recipe}{of brownies, above}
\ingr{1 \fracH}{oz}{unsweetened chocolate}
\ingr{\fracQ}{c}{evaporated milk}
\ingr{\fracT}{c}{sugar}
\end{ingredients}

\begin{recipe}
  \begin{enumerate}
  \item Prepare the brownies and allow them to cool completely.  Don't cut them yet.

  \item To prepare the frosting, melt the chocolate in the top of a double
boiler placed over simmering water.

\item Pour the evaporated milk into an electric blender and add the sugar
and the melted chocolate.  Blend the frosting on medium-low speed
until it thickens, about 50 seconds (the sound of the machine will
change when this process occurs).

\item Using a frosting spatula, spread the frosting evenly over the surface
of the cooled brownies, and allow them to sit for 1 hour before
cutting.
  \end{enumerate}
\end{recipe}
                                                                                

