\dish{Jacques Torres Chocolate Chip Cookies}
\altdish{Chocolate Chip Cookies, Jacques Torres}
\altdish{Cookies, Jacques Torres, Chocolate Chip}
%\serves{}
\makes{18 15~cm cookies}
\prep{45 minutes plus 24 hours to chill}
\source{nyt}

\begin{ingredients}
  \ingr{241}{g}{cake flour (8.5 oz = 2 c minus 2 \tbsp)}
  \ingr{241}{g}{bread flour (8.5 oz = 1 \fracTT\ c)}
  \ingr{1\fracQ}{\tsp}{baking soda}
  \ingr{1\fracH}{\tsp}{baking powder}
  \ingr{1\fracH}{\tsp}{coarse salt}
  \ingr{283}{g}{butter (10 oz = 2\fracH\ sticks)}
  \ingr{283}{g}{light brown sugar (10 oz = 1\fracQ\ c)}
  \ingr{228}{g}{granulated sugar (8 oz = 1 c + 2\tbsp)}
  \ingr{2}{}{large eggs}
  \ingr{2}{\tsp}{vanilla extract}
  \ingr{567}{g}{bittersweet chocolate, at least 60\% cocoa content (1\fracQ\ pounds)}
  \ingr{}{}{sea salt}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Sift flours, baking soda, baking powder, and salt into a bowl.
    Set aside.

  \item   Using a mixer fitted with paddle attachment, cream butter
    and sugars together until very light, about 5 minutes. Add eggs,
    one at a time, mixing well after each addition. Stir in the
    vanilla. Reduce speed to low, add dry ingredients and mix until
    just combined, 5 to 10 seconds. Drop chocolate pieces in and
    incorporate them without breaking them. Press plastic wrap against
    dough and refrigerate for 24 to 36 hours. Dough may be used in
    batches, and can be refrigerated for up to 72 hours.

  \item   When ready to bake, preheat oven to \FC{350}{175}. Line a
    baking sheet with parchment paper or a nonstick baking mat. Set
    aside.

  \item   Scoop 6 3 1/2-ounce (100~g) mounds of dough (the size of generous
    golf balls) onto baking sheet, making sure to turn horizontally
    any chocolate pieces that are poking up; it will make for a more
    attractive cookie. Sprinkle lightly with sea salt and bake until
    golden brown but still soft, 18 to 20 minutes. Transfer sheet to a
    wire rack for 10 minutes, then slip cookies onto another rack to
    cool a bit more. Repeat with remaining dough, or reserve dough,
    refrigerated, for baking remaining batches the next day. Eat warm,
    with a big napkin.

  \end{enumerate}

  For 50~g cookies (makes 36), bake for 16~minutes.

  For 25~g cookies, (makes 72--75), bake for 13 minutes.
\end{recipe}
