\dish{Maury Rubin's Grilled Chocolate Sandwich}
\altdish{Grilled chocolate sandwich}
\makes{6--8 sandwiches}
\prep{}
\sourceD{nyt}{7 September 2003}

\begin{ingredients}
  \ingr{8}{oz}{dark (bittersweet) chocolate}
  \ingr{\fracH}{c}{heavy cream}
  \ingr{12--16}{}{slices plain white bread}
  \ingr{}{}{a handful of chocolate}
  \ingr{}{}{\fracH long batons of chocolate or chocolate chips (about \fracT cup)}
  \ingr{3--4}{Tbsp}{softened butter}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}
  \item Chop the chocolate
    fine and set aside in a medium bowl.

\item Heat the cream in a small saucepan until just boiling
and pour over the chopped chocolate. Let stand 1 minute,
then whisk until smooth. Refrigerate until just slightly
solid, about 30 minutes.

\item Spread a layer of the chocolate mixture \fracQ-inch thick
(approximately 2 to 3 tablespoons) on half the bread sides
to within about \fracQ inch of the edges. Press about 2
teaspoons of the chocolate chips (or 5 or 6 pieces of
batons) into the center of each filling.

\item Spread a bit of softened butter over one side of the
remaining slices. Buttered side up, place the slice over   
each chocolate-spread slice and press lightly around the   
edges to seal. Refrigerate for at least 15 minutes before
putting on a grill or on a press. (If you are using a
skillet instead, freeze the sandwich 15 minutes.)

\item Heat a grill or sandwich press (or a large griddle or
skillet over medium-high heat), and add the sandwiches.
Press on one side only for a minute or two (depending on   
the particular grill or press you're using) until the bread
is nicely browned; the chocolate should be barely melted
and not swimming out the side. If you are using a griddle
or skillet, heat the sandwich first on the unbuttered side
until lightly toasted, about 1 minute; turn the sandwich
over and weight it down by placing a baking sheet or pan on
top of the sandwich and placing a few soup cans on top.
Toast for another minute, until golden. Cut in half and
finish with a frilled toothpick.



  \end{enumerate}
\end{recipe}

