\dish{Ice Cream}
%\altdish{}
%\serves{}
\makes{1 litre}
\prep{20 minutes plus time to freeze and purée}
\source{nyt}

\stage{Base}

\begin{ingredients}
  \ingr{2}{c}{heavy cream}
  \ingr{1}{c}{whole milk}
  \ingr{\fracTT}{c}{sugar}
  \ingr{\fracE}{\tsp}{fine sea salt}
  \ingr{6}{}{egg yolks (american large)}
  \ingr{}{}{flavoring, see below}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item In a small pot, warm cream, milk, sugar, and salt until
    sugar completely dissolves, about 5~minutes.  Remove pot from
    heat.

  \item In a separate bowl, whisk the yolks.  Slowly whisk about a
    third of the hot cream into the yolks, then whisk the yolk mixture
    back into the pot with the cream. Return pot to medium-low heat
    and gently cook until mixture is thick enough to coat the back of
    a spoon, about \CF{76}{170}.  That is, make a crème anglaise.

  \item Strain through a fine-mesh sieve into a bowl. Cool mixture to
    room temperature. Cover.

  \item \textbf{If using an ice cream maker,} chill at least 4~hours
    before churning.

  \item \textbf{If using a stand mixer,} freeze, removing to beat the
    mixture after about two hours, then one hour, then about a half
    hour, just to avoid the mixture becoming too hard to beat; then
    beat a final time just before serving.

  \item \textbf{If using a food processor,} freeze flat in a large
    ziploc bag, then break apart in the bag before dropping the chunks
    into the food processor.  Process on high until the mixture is
    smooth.

  \end{enumerate}
\end{recipe}

\stage{Aromatics}

\textbf{Vanilla or green tea.}  Scrape 2~vanilla beans into
the cold milk.  Or \fracQ~cup green tea leaves.  Let the custard steep
off the heat for 30~minutes before straining.

\textbf{Mint or basil.}  Pulse together 1~cup clean and dry leaves
with \fracTT~cup sugar until pulverized and bright green.  Use in
place of sugar in base.  Let custard steep 30~minutes before
straining.

\textbf{Cinnamon.}  Break a 10~cm cinnamon stick, preferably a
fragrant variety like Ceylon or canela, into a food processor with
\fracTT~cup sugar until finely ground.  Use in place of sugar in base.
Let custard steep 30~minutes before straining.

\textbf{Lemon or lime.}  In a food processor puls zest of 3~lemons or
limes with \fracTT~cup sugar until smooth and brightly colored.  Use
in place of sugar in base.  Let custard steep 30~minutes before
straining.  Stir in the juice and zest of 1~lemon or lime before
chilling.

\textbf{Strawberry or raspberry.}  Make the base without milk. In a
blender, purée 450~g berries, 3~\tbsp~sugar, \fracH~\tsp~lemon juice
or balsamic vinegar and a pinch of salt. Taste; add more sugar and/or
lemon or vinegar if necessary. Purée should be on the sweet side, with
some underlying tartness. Stir into base before chilling. Strain
before churning if using raspberries.

\textbf{Peach or apricot.}  Pit and dice 3~pounds (1360~g) peaches or
apricots (no need to peel them). In a saucepan over medium heat,
gently simmer fruit with \fracH~cup sugar until fruit is tender, about
10~minutes. Purée in a food processor or blender. Make the base
without milk. Stir \fracH~cup buttermilk and the fruit purée into
warm, strained base. Add a few drops of almond extract if
desired.

\textbf{Cherry.}  In a saucepan over medium heat, simmer 6~cups pitted
cherries (from 2~pounds) with \fracT~cup sugar until cherries are very
soft, about 10~minutes. Purée in a food processor or blender. Make the
base without milk. Stir \fracH~cup buttermilk and the cherry purée
into warm, strained base. Add a few drops of kirsch if desired.

\textbf{Banana.}  In a blender, purée 4 very ripe medium bananas, 2
tablespoons sugar, 1 teaspoon lemon juice and a pinch of salt until
smooth. Make the base without milk. Stir \fracH~cup buttermilk and the
fruit purée into warm, strained base. Add a few drops of vanilla
extract if desired.

\textbf{Chocolate.}  In a saucepan, bring \fracQQ~cup cream and
3~\tbsp~cocoa powder to a simmer. Put 1~cup chopped dry chocolate
(coeur de guanaja) in a mixing bowl with 40~g unsweetened chocolate.
Pour hot cocoa cream over chocolate and stir until melted and smooth.
Stir chocolate mixture and 1 teaspoon vanilla extract into base.
Strain.

\textbf{Chocolate, original version.}  In a saucepan, bring
\fracQQ~cup cream and 3~\tbsp~Dutch-processed cocoa powder to a
simmer. Put 1~cup chopped chocolate in a mixing bowl. Pour hot cocoa
cream over chocolate and stir until melted and smooth. Make base using
1\fracH~cups milk, \fracQQ~cup sugar and no cream. Stir chocolate
mixture, \fracQQ~cup crème fraîche or sour cream and 1 teaspoon
vanilla extract into base. Strain

%\accord{}
