\dish{Grand Marnier Ice Cream}
\altdish{Ice Cream, grand marnier}
%\serves{}
\makes{1 litre}
\prep{20 minutes plus time to freeze and purée}
\source{jma}

\stage{Base}

\begin{ingredients}
  \ingr{450--500}{ml}{heavy cream}
  \ingr{160}{g}{sugar}
  \ingrS{pinch}{}{fine sea salt (\fracE{} \tsp)}
  \ingrS{3}{}{egg yolks}
  \ingr{160}{ml}{water}
  \ingrS{80}{ml}{grand marnier}
  \ingrS{1}{\tsp}{orange extract}
  \ingr{60}{g}{Italian meringue~(page \pageref{label:meringue-italienne-gelato})}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item In a small pot, warm cream, milk, sugar, and salt until sugar
    completely dissolves.  Remove pot from heat.

  \item In a separate bowl, whisk the yolks.  Slowly whisk about a
    third of the hot cream into the yolks, then whisk the yolk mixture
    back into the pot with the cream. Return pot to medium-low heat
    and gently cook until mixture is thick enough to coat the back of
    a spoon, about 78\degreeC.  That is, make a crème anglaise.

  \item Strain through a fine-mesh sieve into a bowl. Cool mixture to
    room temperature. Cover and chill.
    
  \item Combine water and grand marnier.  Cover and chill.

  \item In the sorbetière, combine custard, grand marnier mixture, and
    the orange extract.

  \item As the mixture begins to thicken, add the meringue.

  \end{enumerate}
\end{recipe}

Questions:
\begin{itemize}
\item Is the right amount of orange extract perhaps closer to 2~\tsp?
\item Is the right proportion of grand marnier perhaps closer to \fracT--\fracTT?
\end{itemize}


%\accord{}
