\dish{Kouign Amann}
\altdish{}
%\serves{}
\makes{8}
\prep{4.5~hours}
\source{kitchen-kouign-amann}

\begin{ingredients}
  \ingr{230}{ml}{water (1 cup)}
  \ingr{8}{g}{yeast (2 \tsp)}
  \ingr{310}{g}{flour (T65) (2 \fracH cup)}
  \ingr{6}{g}{salt (1 \tsp)}
  \ingr{230}{g}{salted butter (8 oz)}
  \ingrS{300}{g}{sugar (1 \fracH cup) \textit{(verify)}}
  \ingr{}{}{flour, sugar (for dusting)}
  \ingr{}{}{salted butter (for pans)}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Combine water and yeast, let stand a few minutes.  Add flour
    and salt.  Stir to shaggy mass, then knead 3--4 minutes until
    dough is tacky but smooth.
    
  \item Let rise, covered, 1~hour.  Chill at least 30~minutes.
    
  \item Knead cold butter.  Sprinkle work surface with 1--2~\tbsp of
    reserved flour and roll out the butter to $15\times 25$~cm.
    Replace butter in refrigerator.
    
  \item Roll out dough (dusted with more of reserved flour) to
    $30\times 50$~cm.  Place the butter on the dough to form three
    thirds.  Wrap the butter in the dough (two layers of dough on top,
    one under).
    
  \item Roll the dough slightly to press the layers together, then
    fold again in thirds.
    
  \item Dust table with flour.  Make two turns, then film and
    refrigerate at least 30~minutes.
    
  \item Roll out dough, sprinkle with half of sugar and roll gently to
    help the sugar stick, fold (third turn), then make one more turn
    using the other half of the sugar.  Film and refrigerate.
    
  \item Butter 8~mini-tart pans.  \textit{(The original recipe
      suggested 12.)}
    
  \item Dust working surface with a bit of extra sugar.  Dust dough
    with sugar.  Roll dough to $20\times 60$~cm.  It should be about
    7~mm thick.  Cut in $2\times 4$~rectangles.  Fold each by bringing
    the corners to the centre.  Place in the tart pans.
    
  \item Film loosely and let rise 30--40~minutes.
    
  \item Preheat oven to \CF{205}{400}.  Place kouign amann in oven and
    reduce heat to \CF{175}{350}.  Bake 40~minutes until just golden
    without excessive browning.
    
  \item Remove from oven and allow to stand until butter is
    re-absorbed.  Only then move to cooling rack.  Remove before
    completely cool, however, in order to avoid sticking to the pan.
    
  \item Best eaten the same day.

  \end{enumerate}
\end{recipe}

%\accord{}
