\dish{Warm Soft Chocolate Cake}
\altdish{Chocolate cake, warm soft}
\altdish{Cake, chocolate, warm soft}
\makes{4}
\prep{30 minutes plus 12 minutes to bake}
\source{jgv}

\begin{ingredients}
  \ingr{4}{oz}{(113~g) butter (plus a little for buttering pans)}
  \ingr{2}{tsp}{flour (plus a little for dusting pans)}
  \ingr{4}{oz}{bittersweet chocolate}
  \ingr{2}{}{eggs}
  \ingr{2}{}{egg yolks}
  \ingr{\fracQ}{c}{sugar}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Butter and lightly flour 4 4-ounce molds, custard cups,
  ramekins, or similar containers.  Tap out the excess flour.  Preheat
  the overn to 450 $^\circ$F.

\item  Gently heat the butter and chocolate together until chocolate
  is almost completely melted.

\item Beat eggs, yolks, and sugar together with a whisk or electric
  beater until light and thick.

\item Beat melted chocolate and butter together.  While it is still
  warm, pour into the egg mixture, then quickly beat in the flour
  until combined.
  
\item Divide batter among the molds.  (At this point, you can
  refrigerate the desserts for several hours until ready to eat.  Bring
  them back to room temperature before cooking.)

\item Bake molds on a tray for 12 minutes.  The center will still be
  quite soft, but the sides will be set.

\item Invert each mold onto a plate and let sit for about 10 seconds.
  Unmold by lifting up one corner of the mold; the cake will fall out
  onto the plate.  Serve immediately.

  \end{enumerate}

  This is better with 2--4 oz extra chocolate mixed in---the result is
  smoother and creamier, less dry.

\end{recipe}
