\dish{Red Lentil Soup with Lime}
\altdish{Lentil Soup with Lime}
\serves{4--6}
\prep{45 minutes}
\source{madison.VCfE}

\begin{ingredients}
  \ingr{2}{c}{split red lentils, picked over and rinsed several times}
  \ingr{1}{Tbsp}{turmeric}
  \ingr{4}{Tbsp}{butter}
  \ingr{}{}{salt}
  \ingr{1}{}{large onion, finely diced, about 2 cups}
  \ingr{2}{tsp}{ground cumin}
  \ingr{1\fracH}{tsp}{mustard seeds or 1 tsp ground mustard}
  \ingr{1}{}{bunch chopped cilantro, about 1 cup}
  \ingr{3}{}{limes, juiced}
  \ingr{1}{}{large bunch spinach leaves, chopped into small pieces}
  \ingr{1}{c}{cooked rice}
  \ingr{4--6}{Tbsp}{yogurt}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Put the lentils in a soup pot with 2\fracH quarts water, the
    turmeric, 1 tablespoon of the butter, and 1 tablespoon salt.
    Bring to a boil, then lower the heat and simmer, covered, until
    the lentils are soft and falling apart, about 20 minutes.  Puree
    for a smooth and nicer-looking soup.

  \item Meanwhile, in a medium skillet over low heat, cook the onion
    in 2 tablespoons of the remaining butter with the cumin and
    mustard, stirring occasionally.

  \item When soft, about the time the lentils are cooked or after 15
    minutes, add the cilantro and cook for a minute more.

  \item Add the onion mixture to the soup, then add the juice of 2
    limes.  Taste, then add more if needed to bring up the flavors.
    The soup should be slightly sour.

  \item Just before serving, add the last tablespoon of butter to a
    wide skillet.  When foamy, add the spinach, sprinkle with salt,
    and cook just long enough to wilt.  If the rice warm, place a
    spoonful in each bowl.  If it's leftover rice, add it to the soup
    and let it heat though for a minute.

  \item Serve the soup, divide the spinach among the bowls, and swirl
    in a spoonful of yogurt.

  \end{enumerate}
\end{recipe}
