\dish{Mediterranean Lentil Salad}
\altdish{Lentil salad, mediterranean }
\serves{6}
\prep{40 minutes to prepare, plus several hours to chill}
\source{still:life}

\begin{ingredients}
  \ingr{2}{c}{dried lentils}
  \ingr{\fracQ}{c}{olive oil}
  \ingr{\fracQ}{tsp}{salt}
  \ingr{1 to 2}{}{oranges, peeled and sectioned}
  \ingr{1}{}{large clove garlic, crushed}
  \ingr{3}{Tbsp}{fresh lime juice}
  \ingr{3}{Tbsp}{balsamic vinegar (cider vinegar will also work)}
  \ingr{\fracQ}{c}{very finely minced red onion}
  \ingr{\fracQ to \fracH}{tsp}{grated orange rind}
  \ingr{\fracQ to \fracH}{tsp}{grated lime rind}
  \ingr{\fracH}{c}{(packed) dried currants}
  \ingr{1}{}{small carrot, finely minced}
  \ingr{\fracH}{}{red bell pepper, minced}
  \ingr{\fracH}{}{yellow bell pepper, minced}
  \ingr{}{}{a handful each of finely minced fresh parsley, chives, and mint}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}
  \item Rinse the lentils in a colander.  Meanwhile, set a large
    potful of water to boil---at least six cups of water.  After the
    water has reached the boiling point, lower the heat to a simmer.
    Add the lentils and cook very gently in the simmering water,
    partially covered, until they are tender. (Try to prevent the
    water from getting agitated while the lentils are cooking, as that
    will cause them to burst and lose their shape. The goal is to have
    perfectly cooked lentils---light and distinct.) Cooking time
    should be around 20 to 30 minutes. check the water level and add
    more if necessary. Drain the lentils when they are done and gently
    rinse in cold water. Drain again and place in a large bowl.

\item Add remaining ingredients except bell pepper and fresh herbs,
  cover tightly, and chill at least 4 hours.

\item Add the bell pepper and herbs within an hour of serving.
  \end{enumerate}
\end{recipe}
