\dish{Pomelo Salad}
\altdish{Salad, pomelo}
\serves{4}
\prep{2 hours}
\source{jma}


stage{Salad}

\begin{ingredients}
  \ingr{1}{}{pomelo}
  \ingr{1\fracH}{tsp}{sugar}
  \ingr{}{}{juice from 1 lime}
  \ingr{1\fracH}{Tbsp}{chopped fresh corriander}
  \ingr{1}{}{head red leaf lettuce (for garnish)}
  \ingr{\fracQ}{c}{chopped roasted peanuts}
  \ingr{}{}{crispy fried shallots}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Peel and separate pomelo into segments.  Remove the membranes,
    seed, and gently flake the flesh apart into a bowl.  (This can
    take nearly two hours.)  Chill.

  \item In a small bowl mix together the sugar, lime juice, and
    coriander.  Toss with the chilled pomelo.

  \item Arrange the lettuce on a serving platter.  Put the fruit
    mixture over the lettuce.  Top with peanuts and crispy fried
    shallots.

  \end{enumerate}
\end{recipe}

Note: Grapefruit may be substituted for pomelo, but it is nearly
impossible to segment a grapefruit properly, as it is so much more
moist.


\stage{Crispy Fried Shallots}

\begin{ingredients}
  \ingr{6}{}{shallots}
  \ingr{1}{c}{vegetable oil}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Slice shallots into thin slices.  Be sure they are all the
    same thickness to ensure even cooking.

  \item Heat a pan with the vegetable oil over medium heat. Add
    shallots and fry slowly until browned and crisp, 5 to 10 minutes.
    The moisture in the shallots should be completely cooked out.

  \item Drain on paper towel. Store in an air-tight container.  Will
    keep several weeks.

  \end{enumerate}
\end{recipe}

