\dish{Spicy Quinoa, Cucumber and Tomato Salad}
\altdish{Quinoa, Cucumber and Tomato Salad}
\altdish{Cucumber and Tomato Salad with Quinoa}
\altdish{Tomato and Cucumber Salad with Quinoa}
\serves{6}
%\makes{}
\prep{45 minutes}
\source{nyt}

\begin{ingredients}
  \ingr{1}{c}{quinoa}
  \ingr{3}{c}{water}
  \ingr{}{}{salt, to taste}
  \ingr{2}{c}{cucumber, diced}
  \ingr{1}{}{small red onion, finely minced}
  \ingr{2}{c}{tomato, finely diced}
  \ingr{1--2}{}{jalape\~{n}o or serrano peppers, to taste, seeded and finely chopped}
  \ingr{\fracH}{c}{coriander leaf, chopped, plus sprigs for garnish}
  \ingr{2}{\tbsp}{fresh lime juice}
  \ingr{1}{\tbsp}{red wine vinegar or sherry vinegar}
  \ingr{3}{\tbsp}{olive oil}
  \ingr{1}{}{avocado, sliced, for garnish}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Place the quinoa in a bowl, and cover with cold water. Let sit
    for five minutes. Drain through a strainer, and rinse until the
    water runs clear. Bring the 3 cups water to a boil in a medium
    saucepan. Add salt (1/2 to 3/4 teaspoon) and the quinoa. Bring
    back to a boil, and reduce the heat to low. Cover and simmer 15
    minutes or until the quinoa is tender and translucent; each grain
    should have a little thread. Drain off the water in the pan
    through a strainer, and return the quinoa to the pan. Cover the
    pan with a clean dishtowel, replace the lid and allow to sit for
    10 minutes. If making for the freezer, uncover and allow to cool,
    then place in plastic bags. Flatten the bags and seal.

  \item Meanwhile, place the finely diced cucumber in a colander, and
    sprinkle with salt. Toss and allow to sit for 15 minutes. Rinse
    the cucumber with cold water, and drain on paper towels. If using
    the onion, place in a bowl and cover with cold water. Let sit for
    five minutes, then drain, rinse with cold water and drain on paper
    towels.

  \item Combine the tomatoes, chiles, cilantro, vinegar, lime juice
    and olive oil in a bowl. Add the cucumber and onion, season to
    taste with salt, and add the quinoa and cilantro. Toss together,
    and taste and adjust seasonings. Serve garnished with sliced
    avocado and cilantro sprigs.
    

  \end{enumerate}
\end{recipe}
