\dish{Mushroom and Cheese P\^at\'e}
\altdish{P\^at\'e, mushroom and cheese}
\altdish{Cheese and mushroom p\^at\'e}
\makes{2 loaves}
\prep{30 minutes plus 1\fracQ hours to bake plus time to chill}
\source{ebf}

\begin{ingredients}
  \ingr{4}{Tbsp}{butter}
  \ingr{3}{c}{chopped onion}
  \ingr{1}{lb}{mushrooms, coarsely chopped}
  \ingr{\fracH}{tsp}{salt}
  \ingr{1}{tsp}{dry mustard}
  \ingr{\fracH}{tsp}{dill weed}
  \ingr{}{}{black pepper}
  \ingr{}{}{cayenne pepper}
  \ingr{3}{Tbsp}{dry white wine}
  \ingr{\fracQ}{c}{wheat germ}
  \ingr{8}{oz}{neufchatel or cream cheese (1 cup)}
  \ingr{1}{lb}{ricotta cheese (2 cups)}
  \ingr{}{}{paprika}
  \ingr{}{}{freshly minced parsley}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item In a large heavy skillet begin cooking the onions in butter over medium heat, stirring occasionally.

  \item After about 5 minutes, when the onions are soft, add the
  mushrooms, salt, dry mustard, dill, black pepper, and cayenne.  Stir
  well and cook uncovered over moderate heat, stirring intermittently
  for another 5 minutes.

\item Add the wine and stir.  Continue to cook for 5 more minutes.

\item Sprinkle in the wheat germ, stirring the mixture as you
  sprinkle.  Stir and cook 1--2 minutes more, then remove from heat.

\item Cut the neufchatel or cream cheese into the hot mixture.

\item Use a blender or a food processor fitted with a steel blade to
  pur\'ee the mixture.  Transfer the pur\'ee to a large mixing bowl.
  Whisk in the ricotta.

\item You can bake the p\^at\'e in a buttered casserole or in 2 loaf
  pans.  If baked in a casserole it will be softer and you can serve
  it in mounds on greens or as a spread.  If baked in loaf pans it
  will be sliceable.  (When using loaf pans, butter them and line them
  with buttered wax paper.  Cool it in the pan, then remove it and
  peel off the paper.)

\item Bake uncovered for 1\fracQ hours at 400\F\ (205\C).

\item Chill before serving.

\item Sprinkle with paprika and parsley.

  \end{enumerate}
\end{recipe}
