\dish{Broccoli and Tofu in spicy peanut sauce}
\altdish{Tofu and broccoli in spicy peanut sauce}
\altdish{Peanut sauce with tofu and broccoli}
\serves{4--5}
\prep{1 hour}
\source{ebf}


\stage{Peanut Sauce:}

\begin{ingredients}
  \ingr{\fracH}{c}{peanut butter (no sugar)}
  \ingr{\fracH}{c}{hot water}
  \ingr{\fracQ}{c}{cider vinegar}
  \ingr{2}{Tbsp}{tamari sauce}
  \ingr{2}{Tbsp}{blackstrap molasses}
  \ingr{\fracQ--\fracH}{tsp}{cayenne pepper}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item In a small suacepan, whisk together the peanut butter and the
    hot water until you have a uniform mixture.

  \item Whisk in the remaining ingredients.  Set aside.

  \end{enumerate}
\end{recipe}



\stage{The Saut\'e:}

\begin{ingredients}
  \ingr{1}{c}{rice}
  \ingr{1}{lb}{fresh broccoli}
  \ingr{3}{Tbsp}{peanut oil}
  \ingr{2}{tsp}{freshly-grated ginger root}
  \ingr{4}{}{medium cloves garlic, minced}
  \ingr{1}{lb}{tofu, cut into small cubes}
  \ingr{}{}{salt}
  \ingr{2}{c}{onion, thinly sliced}
  \ingr{1}{c}{coarsely chopped raw peanuts}
  \ingr{2--3}{Tbsp}{tamari sauce}
  \ingr{2}{}{scallions, freshly minced}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Start cooking rice.

  \item Cut off the bottom half-inch of the broccoli stems.  Shave off
    the tough outer skins of the stalks with a sharp paring knife or a
    vegetable peeler.  Cut the stalks diagonally into thin slices.
    Coarsely chop the flowerettes.  Set aside.

  \item Begin heating the wok (or a large, heavy skillet).  When it is
    hot add 1 Tbsp of the peanut oil  Add half the ginger and half the
    garlic.  Salt lightly.  Saut\'e over medium heat for 1 minute,
    then add the tofu chunks.  Turn the heat up a little and stire-fry
    the tofu for 5--8 minutes.  Transfer it, including whatever liquid
    it might hae expressed, to the saucepanful of peanut sauce.  Mix
    together gently.

  \item Wipe the wok with a paper towel and return it to the stove to
    begin heating once again.  Add the remaining 2 Tbsp of oil to the
    hot wok and follow suit with the remaining ginger and garlic.
    Salt lightly.  Add the onions and grind in some fresh black
    pepper.  Saut\'e, stirring frequently over medium heat until the
    onions are soft, above 5 minutes.

  \item On another burner, begin heating the peanut-tofu sauce on a
    very low flame.  It shouldn't actually cook---it only needs to be
    warmed through.

  \item Add the broccoli and the chopped peanuts to the wok.  Add 2--3
    Tbsp tamari sauce and stir-fry over medium-high heat until the
    broccoli is bright green and just ender, about 5 minutes.

  \item Pour the heated peanut sauce over the saut\'e.  Toss gently
    until everything is coated with everything else.  Sprinkle in the
    minced scallions as you toss.

  \item Serve over rice.

  \end{enumerate}
\end{recipe}
