\dish{Russian Vegetarian Borscht}
\altdish{Cabbage borscht}
\altdish{Borscht, cabbage}
\serves{6}
\prep{}
\source{unknown}

\begin{ingredients}
  \ingr{1}{Tbsp}{vegetable oil}
  \ingr{1}{Tbsp}{butter}
  \ingr{1}{}{onion, chopped}
  \ingr{3}{}{medium size carrots, peeled and sliced}
  \ingr{1}{}{small parsnip, cut into thin 2-inch strips}
  \ingr{3}{}{medium size beets, cut into thin 2-inch strips}
  \ingr{2}{}{large cloves garlic, finely minced}
  \ingr{1}{}{bay leaf}
  \ingr{1}{Tbsp}{sugar}
  \ingr{6}{c}{vegetable or chicken broth}
  \ingr{1}{}{small cabbage, cut into 2-inch chunks}
  \ingr{1}{}{medium size potato, peeled and diced into \fracH-inch pieces}
  \ingr{\fracQ}{c}{tomato pur\'ee}
  \ingr{}{}{salt and freshly ground black pepper to taste}
  \ingr{\fracQ}{c}{Balsamic or red wine vinegar}
  \ingr{}{}{sour cream for accompaniment}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}
  \item   In a Dutch oven, heat oil and butter over medium heat and saute
      onion, carrots, parsnip and beets until onion is translucent.

   \item Stir in the garlic, bay leaf and sugar and cook for 30
      seconds. Add broth, cabbage, potatoes and tomato puree, salt and
      pepper.

   \item Simmer, covered until vegetables are tender, about 20 to 30
      minutes.

   \item Remove from heat and stir in vinegar.

   \item Cool to room temperature and refrigerate overnight.

   \item To serve, ladle cold soup into bowls and place a dollop of sour
      cream on top.

  \end{enumerate}
  
  I like to add lentils to this recipe.  I add uncooked lentils (and
  some extra liquid) just before the long simmer..

\end{recipe}
