\dish{Cheese Strudel}
\altdish{Strudel, cheese}
\serves{6}
\makes{2 rolls}
\prep{1 hour plus 30 minute to bake}
\source{moosewood}


\textbf{Cheese-Rice Filling:}

\begin{ingredients}
  \ingr{3}{c}{cooked brown rice (1\fracH c raw)}
  \ingr{1}{c}{chopped onion}
  \ingr{2}{Tbsp}{butter}
  \ingr{2}{Tbsp}{sesame seeds}
  \ingr{3}{c}{grated cheddar cheese}
  \ingr{}{}{salt and pepper}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Saut\'e onion in butter until soft and translucent.

  \item Add sesame seeds.  Toss and cook for aboiut one minute.

  \item Combine all ingredients.  Add salt and pepper to taste.

  \end{enumerate}
\end{recipe}



\textbf{Broccoli-Cheese Filling:}

\begin{ingredients}
  \ingr{6}{c}{raw, chopped broccoli}
  \ingr{3}{Tbsp}{butter}
  \ingr{2}{}{eggs, beaten}
  \ingr{1}{c}{chopped onion}
  \ingr{2}{c}{bread crumbs}
  \ingr{2}{c}{grated cheddar cheese}
  \ingr{1}{}{lemon (juice from)}
  \ingr{}{}{salt and pepper}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Saut\'e onion in butter with \fracH tsp salt.  When onion is
    soft, add the broccoli.  Salt lightly again and saut\'e until
    broccoli is tender, but still bright green, about 8 minutes over
    medium heat.

  \item Combine all ingredients and season to taste.

  \end{enumerate}
\end{recipe}




\textbf{Making the strudel:}

Either use filo dough (see below) or
\hyperref[pâte-feuilletée]{pâte feuilletée}
(page~\pageref{pâte-feuilletée})

\begin{ingredients}
  \ingr{1}{lb}{filo dough}
  \ingr{\fracQ}{lb}{butter}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Prepare filling.  Preheat oven to \FC{375}{190}.

  \item Melt butter.  Prepare a well-greased tray for baking.  Have at
    the ready a pastry brush, defrosted strudel leaves (unwrapped and
    covered with a slightly damp towel).  Optionally have sesame seeds
    or wheat germ available to sprinkle on top.

  \item On a large, clean working surfafce, place on rectangle of file
    down long direction away from you.  Brush it generously with
    melted butter.  Place another leaf directly on top of the first
    and brush it with more butter.  Continue the layering and
    buttering until you have a pile of four.  Butter the top leaf.

  \item Apply half the filling (half of one recipe) to the pile along
    the near (short) edge.  Leave at least 1\fracH inches free at the
    bottom and sides.  Fold the sides over and gently roll the strudel forward.

  \item Carefully move the strudel to the buttered tray.

  \item Repeat with the other roll.

  \item Brush more butter on finished rolls, sprinkle with sesame
    seeds or wheat germ, make 3 or 4 slashes with a serrated knife on
    a diagonal.

  \item Bake 30 minutes or until golden and crisp.

  \end{enumerate}
\end{recipe}

