\dish{Lentil-Filled Vidalia Onions}
\altdish{Onions, lentil-filled}
\serves{6}
\prep{2 hours}
\source{veg:entertain}


\stage{Vidalia Onion Cups}

\begin{ingredients}
  \ingr{6}{}{Vidalia Onions}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}
  \item Peel the onions and cook them in boiling water to
    cover for 10 minutes.

  \item Drain and let the onions
    sit until they are cool enough to handle.

  \item Scoop
    out the center of each with a spoon, leaving a
    shell 2 layers thick.  Chop the scooped-out
    portion and set it aside for use in preparing the
    lentil filling.

  \end{enumerate}
\end{recipe}


\stage{Papaya Chutney}
\altdish{Papaya chutney}
\altdish{Chutney, papaya}

\begin{ingredients}
  \ingr{4}{}{large ripe papayas, peeled and chopped (see note)}
  \ingr{\fracQ}{c}{lemon juice}
  \ingr{2}{Tbsp}{lemon zest}
  \ingr{1}{c}{golden raisins}
  \ingr{\fracH}{c}{water}
  \ingr{\fracH}{c}{raspberry vinegar}
  \ingr{\fracH}{c}{honey (or \fracTT cup raw (turbinado) sugar}
  \ingr{\fracH}{c}{slivered toasted almonds}
  \ingr{2}{inches}{ginger}
  \ingr{1}{}{large red bell pepper, seeded and chopped}
  \ingr{\fracT}{c}{minced fresh cilantro}
\end{ingredients}

\begin{recipe}
  \begin{enumerate}

  \item Combine all ingredients in a large saucepan.
    Bring to a boil.  Lower heat and simmer for 1
    hour, or until the mixture thickens.

\item Remove from heat and let cool.  Transfer to a jar, cover, and
  refrigerate.

  \end{enumerate}
  
  Note: substitute 5 cups peeled, chopped peaches---fresh or defrosted
  frozen---when papayas are unavailable.

\end{recipe}


\stage{Lentil Filling}

\begin{ingredients}
  \ingr{1}{c}{dried lentils}
  \ingr{2}{c}{chopped reserved onion from the prepared Vidalias, above}
  \ingr{4}{c}{water}
  \ingr{2}{}{garlic cloves, minced}
  \ingr{2}{Tbsp}{unsalted butter or avocado oil}
  \ingr{1}{Tbsp}{ground cumin}
  \ingr{2}{tsp}{ground ginger}
  \ingr{2}{tsp}{paprika}
  \ingr{\fracT}{c}{minced frersh cilantro}
  \ingr{2}{}{fresh tomatoes, peeled, chopped, and drained}
  \ingr{\fracH}{c}{shredded mild white cheese, such as mozzarella or Monterey Jack}
  \ingr{\fracH}{c}{ricotta or small curd cottage cheese}
  \ingr{2}{c}{papaya chutney (below)}
\end{ingredients}

\begin{recipe}
  \begin{enumerate} 

  \item In a medium saucepan, combine the lentils, 1~cup of the
  reserved onion, and water. Bring to a boil, cover, and let simmer
  for about 30 minutes, until the lentils are soft and cooked through.

  \item Drain the lentils and set them aside.

  \item Preheat oven to 375\F\ (190\degreeC).

  \item In a medium saucepan, saut\'e the remaining 1~cup onion and
  the garlic in butter until the onion is soft and translucent.

  \item Add the cumin, ginger, paprika, and cilantro, and continue to
  saut\'e for 3~minutes more.

  \item Add the tomato pulp and reserved lentils and stir to blend.
  Stir in the mozzarella and ricotta and remove from heat.

  \item Fill the onions with the lentil mixture.  Place in the baking
  dish and bake for 45~minutes, until the filling is soft and blended
  together but the shells retain their shape.

  \item Serve topped with papaya chutney.

  \end{enumerate}
\end{recipe}


