\dish{Deep Dish Pizza}
\altdish{Pizza, deep dish, Byron Talbot}
\altdish{Byron Talbot deep dish pizza}
\serves{4}
%\makes{}
\prep{30 minutes + 20 minutes to rise + 30 minutes to bake}
\source{byron.talbott.pizza}

\begin{ingredients}
  \ingr{1}{c}{warm water}
  \ingr{3}{\tbsp}{olive oil}
  \ingr{1}{\tbsp}{sugar}
  \ingr{\fracH}{oz}{dried yeast (14 g)}
  \ingrS{}{}{salt (pinch)}

  \ingr{1}{c}{bread flour}
  \ingrS{\fracH}{c}{semolina flour}

  \ingr{4--5}{\tbsp}{ricotta}
  \ingr{}{}{thyme}
  \ingr{}{}{basil}
  \ingr{2}{c}{mozzarella}
  \ingr{1.5}{c}{marinara}
  \ingr{}{}{parmesan}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Combine water, oil, sugar, yeast, and salt.  Mix for two
    minutes.  Set aside for ten minutes.

  \item Add flours and knead for 5--7~minutes.  Dough will have a
    tacky consistency.  Transfer to a well-oiled bowl (approx 1~\tbsp
    olive oil), coat the dough with oil, and cover with plastic wrap.
    Let rise 20~minutes.

  \item When dough has doubled in size, turn out onto floured work
    surface, sprinkle with flour, and knead 2--3~minutes.  Press the
    dough into a circular shape just smaller than the size of the iron
    skillet (15--20~cm).  Coat the skillet with olive oil using a
    pastry brush, coat with 2~\tbsp semolina, and transfer the dough
    to the skillet.  Press evenly up onto the sides.

  \item Spread ricotta cheese on the bottom, then add thyme and basil,
    then mozzarella and any cooked vegetables, then the marinara, and
    finally the parmesan.

  \item Bake 30--35~minutes at \FC{400}{205}.

  \end{enumerate}
\end{recipe}

I sometimes replace \fracH~c of flour with \fracQQ~c maize meal.

%\accord{}
