\dish{Neapolitan Pizza Dough}
\altdish{Pizza, Neapolitan}
\serves{4--8}
%\makes{}
\prep{1 hour over 50 hours}
\source{modernist.bread}

\begin{minipage}{.45\textwidth}
  Full recipe \\
  (four large or six medium pizzas)

  \begin{ingredients}
    \textbf{Poolish}\\
    \ingr{50}{g}{water}
    \ingr{50}{g}{bread flour}
    \ingrS{0.05}{g}{instant dry yeast}
    \textbf{Dough}\\
    \ingr{360}{ml}{water}
    \ingrS{3}{g}{instant dry yeast}
    \ingr{500}{g}{bread flour}
    \ingrS{10}{g}{diastatic malt powder}
    \ingr{11}{g}{salt}
    \ingr{5}{g}{olive oil}
  \end{ingredients}
\end{minipage}
\begin{minipage}{.45\textwidth}
  Half recipe \\
  (four small pizzas)

  \begin{ingredients}
    \textbf{Poolish}\\
    \ingr{25}{g}{water}
    \ingr{25}{g}{bread flour}
    \ingrS{0.02}{g}{instant dry yeast}
    \textbf{Dough}\\
    \ingr{180}{ml}{water}
    \ingrS{1.5}{g}{instant dry yeast}
    \ingr{250}{g}{bread flour}
    \ingrS{5}{g}{diastatic malt powder}
    \ingr{5.5}{g}{salt}
    \ingr{2.5}{g}{olive oil}
  \end{ingredients}
\end{minipage}


\begin{recipe}
  \begin{enumerate}

  \item \textbf{Poolish:} Combine flour and water with a pinch of
    yeast (first three ingredients), stir well and ferment 12~hours.

  \item \textbf{Dough:} Combine water and yeast.  Stir to dissolve
    yeast.  Add poolish.  Add flour and water.  Mix to shaggy mass.

  \item Add salt and olive oil.  Mix on medium speed to full gluten
    development.

  \item Bulk ferment 1\fracH{} hours.

  \item Divide and form boules.  Place in oiled and covered bowls in
    the refrigerator and allow to proof for 1--2~days.

  \item Remove dough 90 to 120~minutes before shaping.  Preheat a
    pizza stone for one hour prior to baking.

  \item Shape pizza by stretching it, not rolling.  Using gravity and
    working around the edge is far easier than spinning.

  \item Place each pizza dough on baking parchment, spread
    \hyperref[tomato.sauce]{tomato sauce} (p.~\pageref{tomato.sauce})
    and slices of drained mozzarella cheese.  Bake immediately.

  \item Top with 1~g of basil immediately after baking.

  \end{enumerate}
\end{recipe}

\notes
\begin{itemize}
\item Count roughly 75~g of tomato sauce for a 250~g dough.
\item Preheat pizza stone to maximum oven temperature.
\item The pizza stone should be 20~cm from the broiler.
\item 5~minutes before baking, switch to high temperature broiler.
\item Insert the pizza in the oven (directly on the baking stone, or
  at least with only baking parchment in between).
\end{itemize}
