\dish{Potato Torte}
\serves{12--16}
\prep{1 hour to prepare, 1 1/4 hour to bake, at least 1 hour to cool}
\source{veg:entertain}

\begin{ingredients}
\ingr{2}{}{medium white onions, chopped (about 300 g)}
\ingr{3}{T}{olive oil}
\ingr{4}{cups}{canned Italian plum tomatoes, drained and coarsely
  chopped (about 3~kg canned before draining)}
\ingr{}{}{Freshly ground black pepper to taste}
\ingr{}{}{Butter for pan}
\ingr{8}{}{large potatoes, boiled and peeled (about 1300~g)}
\ingr{4}{}{large eggs, lightly beaten}
\ingr{1 1/4}{cups}{diced fresh mozzarella cheese (about 220~g)}
\ingr{1 1/4}{cups}{diced provolone cheese (about 140~g)}
\ingr{1}{cup}{freshly grated Parmesan or Asiago cheese (about 110~g)}
\ingr{$\frac 2 3$}{cup}{fresh parsley, minced}
\ingr{$\frac 1 2$}{cup}{fresh oregano; or 1 T dried oregano, crumbled}
\ingr{2}{T}{extra-virgin olive oil}
\end{ingredients}

\begin{recipe}

  \begin{enumerate}

  \item Preheat the oven to 350 F.
    
  \item Saute the onion in 3 T olive oil until soft and translucent.  Add the
    tomatoes and pepper to taste.  Cook over medium heat until the tomato
    sauce is thick and smooth, 10 to 15 minutes.
    
  \item Mash the potatoes until smooth.  Beat in the eggs, mozzarella,
    provolone, Parmesan or Asiago, parsley, and oregano.  Mix well.
    
  \item Generously butter a 12-inch springform pan (or a 9 $\times$ 13 metal pan).
    Spread one-third of the potato mixture evenly over the bottom of the
    pan.  Cover with half of the tomato sauce.  Smooth on another
    one-third of the potato mixture, and cover with the rest of the
    sauce.  Top with the remaining potato mixture.
    
  \item Drizzle the torte with extra-virgin olive oil and bake at 350 F for 1
    hour.  Cover the top with foil and bake 15 to 20 minutes more, or
    until a knife tests clean.
    
  \item Cool to room temperature and serve, or refrigerate the torte several
    hours or overnight and serve at room temperature or chilled.
  \end{enumerate}

\end{recipe}
