\dish{Prakus}
\altdish{Stuffed cabbage}
\altdish{Cabbage stuffed with lentil balls}
%\serves{}
%\makes{}
\prep{1 hour(?) plus about two hours to cook}
\source{ssa,sadie:horwitz}

\stage{Original Recipe}

This recipe needs to be converted: some combination of lentils, wheat,
eggs, mushroom, etc., ought to make a good center ball.

\begin{ingredients}
  \ingr{1}{}{cabbage}
  \ingr{2}{lbs}{ground meat}
  \ingr{}{}{salt and pepper}
  \ingr{1}{}{egg}
  \ingr{}{}{bread crumbs}
  \ingr{1}{}{onion}
  \ingr{1}{can}{tomato soup}
  \ingr{1}{}{large can tomato sauce}
  \ingr{2}{Tbsp}{vinegar}
  \ingr{2}{Tbsp}{sugar}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Core cabbage.  Boil cabbage to make it less brittle.  Keep water.

  \item Combine meat, bread crumbs, egg, salt, and pepper.

  \item Saut\'e onions in large cooking pot.  Add tomato soup, tomato sauce,
    vinegar, and sugar.  Add some water from cabbage.

  \item Form meatballs and wrap in cabbage leaves.  Place in sauce.
    Add more water if needed.

  \item Simmer until cabbage is brownish and cooked, a couple hours.

  \end{enumerate}
\end{recipe}


\stage{Vegetarian Prakus}
\altdish{Prakus, vegetarian}

\source{jma}

\begin{ingredients}
  \ingr{1}{}{cabbage}
  \ingr{2}{c}{red lentils, dry, cooked}
  \ingr{1}{c}{green lentils, dry, cooked}
  \ingr{}{}{butter}
  \ingr{2}{}{red onions}
  \ingr{3}{}{cloves garlic}
  \ingr{10}{oz}{mushroom, chopped}
  \ingr{28}{oz}{crushed tomato}
  \ingr{8}{oz}{tomato paste}
  \ingr{1}{}{potato, boiled, lightly mashed}
  \ingr{1\fracH}{Tbsp}{garam masala}
  \ingr{1\fracH}{tsp}{ground cloves}
  \ingr{}{}{salt and pepper}
  \ingr{2}{}{eggs}
  \ingr{2}{Tbsp}{vinegar}
  \ingr{2}{Tbsp}{sugar}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Core cabbage.  Boil cabbage until soft.  Do not overboil or
    the leaves will not have the strength to be used as wrappings.
    Reserve the water from the cabbage, but remove the cabbage so it
    can drain and cool.

  \item Cook lentils.  Note that green lentils take longer to cook, so
    either start them first and then add red or else cook separately.

  \item Saut\'e onions in butter.  Add garlic.  Add mushrooms and
    simmer.

  \item Add crushed tomato, tomato paste, potato, and spices.  Add some of the
    water from the cabbage if necessary.  Simmer ten more minutes.

  \item Add lentils, remove more solid portion to a bowl and let
    cool.  Reserve more liquid portion for sauce.  The sauce will have
    vegetables and lentils in it.

  \item Add eggs and mix well.

  \item Form balls and wrap in cabbage leaves.  Place in sauce.
    Add more cabbage water as needed to cover all the wrapped balls.

  \item Simmer until cabbage is brownish and cooked, a couple hours.

  \end{enumerate}
\end{recipe}



This can also be made by shredding the cabbage instead of using it as
a wrapping.  The result is a stew.  To make as a stew, instead of
boiling the cabbage, shred it and add with a little water after the
mushrooms are cooked but before adding the tomato mixture.  Cook until
the cabbage just begins to wilt, then add tomato, etc.

Don't form balls, but do let cook over low heat for an hour or more.


\bigskip

I consider this recipe still in the experimental stage.
