\dish{Souffl\'e au ma\"is, fromage, tomates, et cerfeuil}
\altdish{Corn, cheese, tomato, and chervil souffl\'e}
\serves{2--4}
%\makes{}
\prep{30 minutes + 30 minutes to cook}
\source{veg:bistro}

\begin{ingredients}
  \ingr{5}{}{egg whites}
  \ingr{}{}{pinch of salt}
  \ingr{3}{}{egg yolks}
  \ingr{}{}{butter}
  \ingr{2}{\tbsp}{grated Parmesan cheese}
  \ingr{4}{}{ripe tomatoes, diced}
  \ingr{}{}{corn (fresh, 1 ear; or a small can, drained)}
  \ingr{2}{cloves}{garlic}
  \ingr{1\fracH}{c}{shredded gruy\`ere (170 g)}
  \ingr{}{}{large pinch cumin seeds}
  \ingr{}{}{cayenne pepper or Tabasco sauce to taste}
  \ingr{1--2}{\tbsp}{chervil}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Preheat oven to \FC{425}{218}.

  \item Separate the eggs.  Beat the egg whites and salt until stiff,
    glossy peaks form.

  \item Optionally, beat the egg yolks until white and foamy.

  \item Butter a 4-cup souffl\'e dish or 4 individual  1-cup souffl\'e
    dishes and coat the inside with the Parmesan cheese.

  \item Mix the egg yolks with the tomatoes, corn, garlic, gruy\`ere, cumin,
    cayenne or Tabasco, and half the chervil.  Stir in one third of
    the beaten egg whites, then fold in the remaining whites.

  \item Pour into the prepared souffl\'e dish and bake for 25~minutes
    or until the souffl\'e is puffed, golden brown, and doesn't jiggle
    too much when lightly disturbed.  (For the individual souffl\'es,
    bake 15--20 minutes.)

  \item Serve immediately, sprinkled with remaining chervil.

  \end{enumerate}
\end{recipe}
