\dish{Souffl\'e aux tomates et poivrons}
\altdish{Tomato and red pepper souffl\'e}
\altdish{Red pepper and tomato souffl\'e}
\serves{2--4}
%\makes{}
\prep{30 minutes + 30 minutes to cook}
\source{veg:bistro}


\textbf{Coulis de Tomates aux Poivrons Rouges}

\begin{ingredients}
  \ingr{2}{}{onions, coarsely chopped}
  \ingr{1}{\tbsp}{olive oil}
  \ingr{3}{cloves}{garlic, minced}
  \ingr{1}{}{red bell pepper, seeded, deribbed, and chopped}
  \ingr{2}{}{fresh tomatoes (or canned), diced}
  \ingr{\fracQ}{c}{tomato juice}
  \ingr{}{}{salt}
  \ingr{}{}{pepper}
  \ingr{}{}{Tabasco sauce or cayenne pepper to taste}
  \ingr{}{Pinch}{sugar if tomatoes are too acidic}
  \ingr{}{Large pinch}{dried thyme, marjoram, savory, or herbes de Provence}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item In a medium, heavy saucepan over medium heat, saut\'e the
    onion in the olive oil until softened, then add the garlic and red
    pepper.  Continue to cook for about 5~minutes, or until the pepper
    begins to soften.

  \item Add the tomatoes.

  \item Cook until the mixture is chunky and almost sauce-like, then
    add the tomato juice and bring to a boil.  Reduce heat, cover, and
    simmer for about 5~minutes, or until the pepper and tomatoes are
    very soft.

  \item Let cool, then pur\'ee.  Season.

  \end{enumerate}
\end{recipe}


\textbf{Souffl\'e}

\begin{ingredients}
  \ingr{}{}{butter}
  \ingr{3--4}{\tbsp}{grated Parmesan cheese}
  \ingr{6}{}{eggs, separated}
  \ingr{}{}{large pinch salt}
  \ingr{3}{c}{coulis de tomates aux poivrons rouges}
\end{ingredients}


\begin{recipe}
  \begin{enumerate}

  \item Preheat oven to \FC{425}{218}.  Butter the mold(s) generously
    and coat with the Parmesan.  Set aside.

  \item Beat the egg whites with the salt until they form stiff,
    glossy peaks.

  \item Beat the yolks (optionally alone until foamy,then) with half
    the coulis.  Then stir in a large spoonful of whites, then fold
    together with remaining whites.

  \item Bake for 15 to 20 minutes or until the souffl\'e is puffed,
    golden brown, and doesn't jiggle too much when lightly disturbed.

  \item Serve immediately, sprinkled with remaining chervil.

  \end{enumerate}
\end{recipe}
